An Executable Formal Semantics For A Functional Actor Language

### 2017-12-20 paper/paper.tex
wip on conclusion

>>>>

In this paper we showed how to define the actor semantics from~\cite{} using the
K framework. We described in detail the syntax and semantics of the language in
K, as well as the configuration for our actor language. We also showed how we
can use K's strictness attributes to emulate the reduction contexts described
in~\cite{}. Finally, we discussed a complicated actor program, the tree product
example, and its encoding in K.

One immediate area for future work includes defining more actor programs and
more in-depth actor programs in K. Having a large test suite of complicated
examples can be used to ensure that the semantics in K and the semantics
from~\cite{} do not have any bugs. It can also be used to determine rule
coverage, affirming that all semantic rules can be applied.

Another area for future work inovlves extending

Finally, an important area for future work involves taking advantage of K's
backend tools for formal analysis, such as proving actor programs correct using
K's verification engine. For verification, K uses reachability logic~\cite{}, a
language-independent formal verification framework. Reachability logic supports
all-path reachability, so it can be used to verify programs involving concurrent
semantics. However, in order to fully take advantage of this verification, one
would need to implement partial-order reduction in K in order to reduce the
state space.
